\vspace{-0.25em}\thetitle

### 2009-07-24 paper.tex
...

The presence of linear structure in the matrix representations of several independent traffic traces immediately raises two significant questions.
The existential question: \emph{Why does this linear structure exist?}
Followed, of course, by the practical question: \emph{How can we exploit this structure?}
Neither question can be answered fully in a single paper, but we will begin to address the existential problem now.
In the rest of the paper we apply this insight to the eminently practical problem of predicting the behavior of individual flows from the observation of only a few of their initial packets.

>>>>

The presence of linear structure in the matrix representations of several independent traffic traces immediately raises two significant questions.
The existential question: \emph{Why does this linear structure exist?}
Followed, of course, by the practical question: \emph{How can we exploit this structure?}
Neither question can be answered fully in a single paper, but we will begin to address the existential problem in the next section.
In the rest of the paper we apply this insight to the eminently practical problem of predicting the behavior of individual flows from the observation of only a few of their initial packets.

\section{Whence Linearity?}

Our answer to the question of why low-dimensional linear structure appears in the feature-frequency representation of network traffic can be posed in the form of a model.
A mixture model, to be specific.

% The question of why we see low-dimensional linear structure in the feature-frequency representation of network traffic is deeply connected to the nature of such linear representations themselves.
% But the answer to the question also requires us to posit a hypothesis about the nature of network traffic.
